
\section{Introduction} \label{sec:Introduction}

Due to its usefulness in the semiconductor industry, silicon is one of the most well-studied and well-udnerstood materials used for classical computers. For quantum computers, a plethora of qubit materials are still being investigated, but it has proven difficult to use silicon due to its .... [insert something]. 

There has been a recent proposal to make use of dopants in silicon to act as qubits \cite{the paper} to implement a version of the surface code. 


We have simulated a probe qubit interacting with four data qubits. The probe qubit is performing a circular orbit $40$ nm above the data qubits, and in this document we will document the effect of various errors. These errors include dephasing, dopan placement uncertainties and a path jitter. 

\subsection{The proposal}
Let us first take a closer look at the scheme proposed in \cite{the paper}. The data qubits are dopants placed in silicon placed in a square pattern using the best dopant placement techniques available, which currently stand at [insert some error value and cite it]. To perform the stabiliser measurements, a probe qubit of a different dopant species is placed on a mobile slab above the data qubits. Each probe qubit performs a stabiliser measurement on four data qubits, a procedure which is performed by physically moving the overhead slab with the probe qubits. 

Some differences in physical parameters are required. 

\subsection{Spin species}

\begin{table}
\begin{tabular}{ccccccccc}
	& $T_1^e$ & $T_2^{e*}$ & $T_2^e$ & $T_{2, decoupl}^e$ & $T_1^N$ & $T_2^{N*}$ & $T_2^N$ & $T_{2, decoupl.}^N$\\ \hline
P (nat. Si, SET) \cite{Pla2012}& $0.7\, $s & $55\, $ns  & $206\, \mu$s & $410\, \mu$s &  & & \\
P (puri. Si, SET) \cite{Muhonen2014}&  & $160\, \mu$s  & $1\, $ms & $560\, $ms & & $500\, \mu$s & $1.75\, $s & $35.6\, $s \\
Bi (puri. Si, CT) \cite{Wolfowicz2013} & $9\, $s &  & $2.7\, $s && && &\\
NV (puri. C, RT) \cite{Balasubramanian2009,Bar-Gill2013} & & & $1.8\, $ms & $3.3\, $ms && &&\\
NV (puri. C, $77\, $K) \cite{Bar-Gill2013} & & &  & $0.6\, $s && &&\\
SiC ($20\, $K) \cite{Christle2014} & & $1.1\, \mu$s & $1.2\, $ms & && && \\
SiC (RT) \cite{Koehl2011} & $185\, \mu$s & $214\, $ns & $40\, \mu$s &  & & && \\
\hline
\end{tabular} 
\label{lala}
\caption{\cite{Pla2012,Muhonen2014}: high field >1T low temp mK. Even good coherenc ebeing close to suurface.}
\end{table}

Donors deep in bulk show longer coherence times $T_2^e=2\, $s \cite{Tyryshkin2011} not applicable for us.

