
\subsection{Spin species}

Having demonstrated how the parity measurement is realised and how long each measurement could take we now look into different available spin systems. 

As shown in the previous sections we require $\Delta d^3/ J > 10^4$. This is achieved by choosing two different spin species for the data and probe qubits. Any sensible combination of species given in Table.\@ \ref*{TAB:qubits} fulfils this criterion.

For the data qubits we desire qubits with long coherence to maintain the quantum information throughout a large number of parity measurements. Furthermore, we only require global control for the data qubits during operation as logical operations on the encoded qubits can be performed using the stabilizer measurements.
In case of the probe qubits we require coherence times which are longer than the time it takes to perform a parity measurement. In addition to that readout is very important and individual control is required.


\begin{table}[H]
	\begin{tabular}{lrrrr}
		\hline
		spin qubit & $T_1$ & $T_2^{*}$ & $T_2$ & $T_{2,\textrm{decoupl}}$ \\ \hline \\
		P (nat. Si, mK, SET) \cite{Pla2012}& $0.7\, $s & $^{10}55\, $ns  & $^5206\, \si{\micro s}$ & $410\, \si{\micro s}$  \\
		P ($^{28}$Si, mK, SET) \cite{Muhonen2014}&  & $^7160\, \si{\micro s}$  & $^41\, $ms & $560\, $ms \\
		P$^{\text{nuc}}$ ($^{28}$Si, mK, SET) \cite{Muhonen2014}& & $500\, \si{\micro s}$ & $1.75\, $s & $35.6\, $s \\
		P ($^{28}$Si, $6.9\, $K, bulk) \cite{Morley2010}& &  & $14\, $ms &  \\
		P ($^{28}$Si, $1.8\, $K, bulk) \cite{Tyryshkin2011}& &  & $0.6\, $s &  \\
		Bi ($^{28}$Si, $4.3\, $K bulk CT) \cite{Wolfowicz2013} & $9\, $s &  & $^12.7\, $s &\\
		NV ($^{12}$C, RT) \cite{Balasubramanian2009,Bar-Gill2013} & & & $^21.8\, $ms & $3.3\, $ms \\
		NV ($^{12}$C, $77\, $K) \cite{Bar-Gill2013} & & &  & $0.6\, $s \\
		SiC ($20\, $K) \cite{Christle2014} & & $^81.1\, \si{\micro s}$ & $^31.2\, $ms &  \\
		SiC (RT) \cite{Koehl2011} & $185\, \si{\micro s}$ & $^9214\, $ns & $^640\, \si{\micro s}$ &   \\
		\hline
	\end{tabular} 
	\caption{Summary of coherence times of various spin qubit systems. The spin species as well as the measurement temperature is given. RT stands for room temperature while CT refers to clock transitions. For donors in Silicon we distinguish between near surface dopants read out using a single-electron-transistor (SET) and bulk dopants. The numbers in superscript refer to fig.\@ \ref{fig:phaseplot}.}
	\label{TAB:qubits}
\end{table}

This illustrates that coherence is an important parameter for choosing a spin system. Dephasing is a reversible loss of coherence due to inhomogeneous broadening which is characterised by the dephasing time $T_2^*$ which is usually much shorter than a millisecond (see Table.\@ \ref{TAB:qubits}). Luckily we should be able to combine the parity measurement with spin echo or even dynamical decoupling techniques enhancing coherence to the more generous time $T_2$ which represents irreversible loss of coherence.

Donors in silicon are excellent candidates for both data and probe qubits as they offer extremely long coherence times when implanted in purified $^{28}$Si (see Table.\@ \ref{TAB:qubits}). Moreover, electrical read out of high-fidelity using a single-eletron-transistor (SET) \cite{Pla2012,Pla2013,Muhonen2014} as well as optical \cite{Lo2015} read out has been demonstrated for $^{31}$P donors and is feasible for $^{209}$Bi. Control of individual spins can be achieved by tuning them in and out of resonance using the stark effect \cite{Pica2014}. The control electronics has a small footprint making a large scale implementation feasible. Being able to transfer the electron spin state to the nuclear spin offers even longer coherence times. Additionally, $^{209}$Bi has several clock transitions (CT) which are insensitive to magnetic fields leading to very long electron spin coherence times ($T_2=2.7\, $s). However, operation in this regime will make the $^{209}$Bi qubit also insensitive to the magnetic dipole-dipole interaction. Tuning in an out of the CT will be necessary to implement the parity measurement. Proof-of-concept implementations could benefit from that fact that donors in silicon even offer moderate coherence times at elevated temperatures. However, the coherence times demonstrated in bulk still remain to be reproduced for near-surface donors as required for this scheme.
Finally, MEMS devices with a sensitivity of \SI{25}{\hertz\per nm} and $0.3\, $nm accuracy \cite{Chu2003} as well as an accuracy of $5\, $nm with a bandwidth of $30\, $Hz have been demonstrated. This gives good prospects for realisation of highly accurate and fast MEMS devices as needed for this scheme in the near future. 

Besides donors in Si we imagine nitrogen vacancies (NV) to be a promising candidate for proof-of-concept demonstrations. NV centres are highly developed qubits \cite{Bar-Gill2013} which offer good coherence times even at room temperature (RT) \cite{Balasubramanian2009}. Individual addressing can be achieved using the stark effect. Optical read out and the possibility of integrating NV centres into an atomic force microscope (AFM) tip makes NV centres good candidates for a probe qubit \cite{Grinolds2013}. The optical read out of NV centres has one drawback as the readout frequency excites carriers in silicon. As a result of this read out has to be performed carefully in safe distance to the data qubits. Additionally diamond MEMS devices still need to be demonstrated.

Recently, defects in SiC have attracted lots of attention \cite{Morello2015} as coherent manipulation of individual spins with predicted room temeprature coherence times on the order of milliseconds has been demonstrated \cite{Widmann2014}. At cryogenic temperatures ($20\, $K) this has already been achieved \cite{Christle2014}. Current experiments still suffered from a low collection efficiency. Having near infra-red transitions, SiC shows excellent prospects for integration with optical fibres. Moreover, AFM tip integration is feasible. However, SiC is still at a very early research stage.  


